---
output:
  word_document: default
  html_document: default
  pdf_document: default
---
Loading the library
```{r}
library(lpSolveAPI)
```
#Primal Problem
Creating an lp with zero constraints and 9 variables
```{r}
rm(Wcorp) # free up resources and memory
Wcorp<-make.lp(0,9)
```
Creating an objective function and setting it for maximization
```{r}
set.objfn(Wcorp,rep(c(420,360,300),3))  # Objective function with 9 decision variables
lp.control(Wcorp,sense='max')
```
Adding the constraints to the problem
```{r}
add.constraint(Wcorp,c(1,1,1),"<=",750,indices = c(1,2,3)) 
add.constraint(Wcorp,c(1,1,1),"<=",900,indices = c(4,5,6))
add.constraint(Wcorp,c(1,1,1),"<=",450,indices = c(7,8,9))
add.constraint(Wcorp,c(20,15,12),"<=",13000,indices = c(1,2,3))
add.constraint(Wcorp,c(20,15,12),"<=",12000,indices = c(4,5,6))
add.constraint(Wcorp,c(20,15,12),"<=",5000,indices = c(7,8,9))
add.constraint(Wcorp,c(1,1,1),"<=",900,indices = c(1,4,7))
add.constraint(Wcorp,c(1,1,1),"<=",1200,indices = c(2,5,8))
add.constraint(Wcorp,c(1,1,1),"<=",750,indices = c(3,6,9))
add.constraint(Wcorp,c(rep(c(900,-750),each=3)),"=",0,indices = c(1:6))
add.constraint(Wcorp,c(rep(c(450,-750),each=3)),"=",0,indices = c(1,2,3,7,8,9))
```
```{r}
solve(Wcorp)
```
```{r}
get.objective(Wcorp)
```
```{r}
get.constraints(Wcorp)
```
```{r}
get.variables(Wcorp)
```
Reduced Cost
```{r}
get.sensitivity.obj(Wcorp)
```
Shadow Prices
```{r}
get.sensitivity.rhs(Wcorp)
```
```{r}
Sens_1<-data.frame(get.sensitivity.rhs(Wcorp)$duals[1:11],get.sensitivity.rhs(Wcorp)$dualsfrom[1:11],get.sensitivity.rhs(Wcorp)$dualstill[1:11])
names(Sens_1)<-c("Price","low","High")
Sens_1
```
```{r}
Sens_2<-data.frame(get.sensitivity.rhs(Wcorp)$duals[12:20],get.sensitivity.rhs(Wcorp)$dualsfrom[12:20],get.sensitivity.rhs(Wcorp)$dualstill[12:20])
names(Sens_2)<-c("Cost","low","High")
Sens_2
```

#Dual Problem
Creating an lp with zero constraints and 11 variables
```{r}
Wcorp1<-make.lp(0,11)
```
Creating objective function and setting it to minimization problem
```{r}
set.objfn(Wcorp1,c(750,900,450,13000,12000,5000,900,1200,750,0,0))
lp.control(Wcorp1,sense='min')
```
Creating Constraints
```{r}
add.constraint(Wcorp1,c(1,20,1,900,450),">=",420,indices = c(1,4,9,10,11))
add.constraint(Wcorp1,c(1,15,1,900,450),">=",360,indices = c(1,4,8,10,11))
add.constraint(Wcorp1,c(1,12,1,900,450),">=",300,indices = c(1,4,7,10,11))
add.constraint(Wcorp1,c(1,20,1,-750),">=",420,indices = c(2,5,9,10))
add.constraint(Wcorp1,c(1,15,1,-750),">=",360,indices = c(2,5,8,10))
add.constraint(Wcorp1,c(1,12,1,-750),">=",300,indices = c(2,5,7,10))
add.constraint(Wcorp1,c(1,20,1,-750),">=",420,indices = c(3,6,9,11))
add.constraint(Wcorp1,c(1,15,1,-750),">=",360,indices = c(3,6,8,11))
add.constraint(Wcorp1,c(1,12,1,-750),">=",300,indices = c(3,6,7,11))
set.bounds(Wcorp1,lower = c(-Inf,-Inf),columns = 10:11)
```
```{r}
solve(Wcorp1)
```

```{r}
get.objective(Wcorp1)
```
```{r}
get.constraints(Wcorp1)
```

```{r}
get.variables(Wcorp1)
```

```{r}
get.sensitivity.obj(Wcorp1)
```

```{r}
get.sensitivity.rhs(Wcorp1)
```
The solution agrees with what we have observed in the primal problem


```

