---
title: "811129289_5"
author: "Purna Sai Kiran, G"
date: "11/8/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Loading required libraries
```{r}
library(lpSolveAPI)
library(Benchmarking)
library(ucminf)
```
Question 1:
DMU1
Formulating a linear model and setting the objective function. This is a maximization problem
```{r}
LP_1<-make.lp(0,4)
lp.control(LP_1,sense="max")
set.objfn(LP_1,c(0,0,14000,3500))
```

Setting constraints
```{r}
add.constraint(LP_1,c(-150,-0.2,14000,3500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_1,c(-400,-0.7,14000,21000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_1,c(-320,-1.2,42000,10500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_1,c(-520,-2.0,28000,42000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_1,c(-350,-1.2,19000,25000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_1,c(-320,-0.7,14000,15000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_1,c(150,0.2),"=",1,indices = c(1,2))

```

Solving the LP problem
```{r}
solve(LP_1)
get.objective(LP_1) 
get.variables(LP_1)
```
The objective value is 1 where we will get maximum efficiency.

DMU2
Formulating an LP and setting the function to maximization
```{r}
LP_2<-make.lp(0,4)
lp.control(LP_2,sense="max")
set.objfn(LP_2,c(0,0,14000,21000))
```

Loading the constraints
```{r}
add.constraint(LP_2,c(-400,-0.7,14000,21000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_2,c(-150,-0.2,14000,3500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_2,c(-320,-1.2,42000,10500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_2,c(-520,-2.0,28000,42000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_2,c(-350,-1.2,19000,25000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_2,c(-320,-0.7,14000,15000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_2,c(400,0.7),"=",1,indices = c(1,2))
```

Solving the LP
```{r}
solve(LP_2)
get.objective(LP_2)
get.variables(LP_2)
```
For DMU 2 also, the maximum efficiency is attained at objective value 1


DMU 3
Formulating an LP and setting the function to maximization
```{r}
LP_3<-make.lp(0,4)
lp.control(LP_3,sense="max")
set.objfn(LP_3,c(0,0,42000,10500))
```
Adding constraints
```{r}
add.constraint(LP_3,c(-400,-0.7,14000,21000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_3,c(-150,-0.2,14000,3500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_3,c(-320,-1.2,42000,10500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_3,c(-520,-2.0,28000,42000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_3,c(-350,-1.2,19000,25000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_3,c(-320,-0.7,14000,15000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_3,c(320,1.2),"=",1,indices = c(1,2))
```
Solving the LP
```{r}
solve(LP_3)
get.objective(LP_3)
get.variables(LP_3)
```
The maximum efficiency is at objective value 1. Inputs are 0.0017 and 0.373 where output is 0.00238 and 0

DMU 4
Formulating the LP with maximization problem
```{r}
LP_4<-make.lp(0,4)
lp.control(LP_4,sense="max")
set.objfn(LP_4,c(0,0,28000,42000))
```
Adding constraints
```{r}
add.constraint(LP_4,c(-400,-0.7,14000,21000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_4,c(-150,-0.2,14000,3500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_4,c(-320,-1.2,42000,10500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_4,c(-520,-2.0,28000,42000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_4,c(-350,-1.2,19000,25000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_4,c(-320,-0.7,14000,15000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_4,c(520,2.0),"=",1,indices = c(1,2))
```
Solving the LP
```{r}
solve(LP_4)
get.objective(LP_4)
get.variables(LP_4)
```
Maximum efficiency is at 1 where the outputs are 0 and 0.0000238 and inputs are 0.000688 and 0.321


DMU 5
Formulating the lp with maximization problem
```{r}
LP_5<-make.lp(0,4)
lp.control(LP_5,sense="max")
set.objfn(LP_5,c(0,0,19000,25000))
```
Adding constraints
```{r}
add.constraint(LP_5,c(-400,-0.7,14000,21000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_5,c(-150,-0.2,14000,3500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_5,c(-320,-1.2,42000,10500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_5,c(-520,-2.0,28000,42000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_5,c(-350,-1.2,19000,25000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_5,c(-320,-0.7,14000,15000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_5,c(350,1.2),"=",1,indices = c(1,2))
```
Solving the LP problem
```{r}
solve(LP_5)
get.objective(LP_5)
get.variables(LP_5)
```
Maximum efficiency is at 1 when the input weights are 0.001 and 0.5 and output weights are 0.00, 0.00

DMU 6
Formulating the LP problem with maximization function
```{r}
LP_6<-make.lp(0,4)
lp.control(LP_6,sense="max")
set.objfn(LP_6,c(0,0,14000,15000))
```
Adding the constraints
```{r}
add.constraint(LP_6,c(-400,-0.7,14000,21000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_6,c(-150,-0.2,14000,3500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_6,c(-320,-1.2,42000,10500),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_6,c(-520,-2.0,28000,42000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_6,c(-350,-1.2,19000,25000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_6,c(-320,-0.7,14000,15000),"<=",0,indices = c(1,2,3,4))
add.constraint(LP_6,c(320,0.7),"=",1,indices = c(1,2))
```
Solving the LP
```{r}
solve(LP_6)
get.objective(LP_6)
get.variables(LP_6)
```
The effieincy is found at objective value 0.8 where the inpu weights are 0.0015 and 0.721 and outputs weights are set to 0.000016 and 0.000042

DAE Analysis
```{r}
X<-matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2.0,1.2,0.7),ncol=2)
Y<-matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol=2)
colnames(X)<-c("Staff","Supplies")
colnames(Y)<-c("Reimbursed_Patients","Paid_Patients")
rownames(X)<-paste0(rep("Facility",6),seq(1,6,1))
rownames(Y)<-paste0(rep("Facility",6),seq(1,6,1))
A <-dea(X,Y,RTS = "crs")
A
B <-dea(X,Y,RTS = "fdh")
B
C <-dea(X,Y,RTS = "vrs")
C
D <-dea(X,Y,RTS = "irs")
D
E <-dea(X,Y,RTS = "drs")
E
F <-dea(X,Y,RTS = "add")
F
G <-dea(X,Y,RTS = "irs2")
G
H <-dea(X,Y,RTS = "fdh+")
H
I <-dea(X,Y,RTS = "vrs+")
I
```

Question 2:
Peers and Lambda Values
```{r}
peers(A)
lambda(A)
peers(B)
lambda(B)
peers(C)
lambda(C)
peers(D)
lambda(D)
peers(E)
lambda(E)
peers(F)
lambda(F)
peers(G)
lambda(G)
peers(H)
lambda(H)
peers(I)
lambda(I)
```
Question 3:

```{r}
M <- cbind(A$eff, B$eff, C$eff, D$eff, E$eff, F$eff)
colnames(M) <- c('CRS Efficiency','FDH Efficiency','VRS Efficiency',
'IRS Efficiency', 'DRS Efficiency', 'FRH Efficiency')
M
```



Question 4:

```{r}
N<-cbind(A$eff,B$eff,C$eff,D$eff,E$eff,F$eff,G$eff,H$eff,I$eff)
colnames(N)<-c(paste0(rep("Q",9),seq(1,7,1)))
N
```
We can see that all facilities are efficient but facility 5 and 6 are inefficient
Facility 5 is efficiency for FDH, VRS, IRS and FRH and for CRS and DRS assumptions it is 97% efficient
Facility 6 is fully efficient for FDH and FRS assumptions. For CRS and DRS it is 86.7% efficient and for IRS and VRS it is 89.6% efficient 


