---
title: "Assignment_6_1"
author: "Purna Sai Kiran, G"
date: "11/21/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Formulating an LP function. We set the function to maximization because we are trying to find the longest route.
```{r}
library(lpSolveAPI)
lproute <- make.lp(0,12)
lp.control(lproute, sense="max")
```
Setting the objective function
```{r}
t_value <- c(5, 3, 4, 2, 3, 1, 4, 6, 2, 5, 4, 7) 
set.objfn(lproute, 1*t_value)
set.type(lproute, 1:12, "binary") 
```
Setting the constraints
```{r}
add.constraint(lproute,c(1,1),"=",1,indices = c(1,2)) 
add.constraint(lproute,c(1,-1,-1),"=",0,indices = c(1,3,4)) 
add.constraint(lproute,c(1,-1),"=",0,indices = c(2,5))
add.constraint(lproute,c(1,-1,-1),"=",0,indices = c(3,6,7))
add.constraint(lproute,c(1,1,-1,-1),"=",0,indices = c(4,5,8,9))
add.constraint(lproute,c(1, -1),"=",0,indices = c(6,10))
add.constraint(lproute,c(1,1,-1),"=",0,indices = c(7,8,11))
add.constraint(lproute,c(1,-1),"=",0,indices = c(9,12))
add.constraint(lproute,c(1,1,1),"=",1,indices = c(10,11,12))
```

Solving the LP Problem
```{r}
solve(lproute)
get.objective(lproute)
get.variables(lproute)
get.constraints(lproute)
```
Mapping input to the output
```{r}
arc <- c("X12", "X13", "X24", "X25", "X35", "X46", "X47", "X57", "X58", "X69", "X79", "X89")
vars<-get.variables(lproute)
output<-data.frame(arc,vars)
output
```
Formulate and solve the binary integer programming (BIP) model for this problem using
library lpsolve or equivalent in R.
From the variables, the longest route will be X12 - X24 - X57 - X79. The maximum objective function is 17