---
title: "Assignment_6"
author: "Purna Sai Kiran, G"
date: "11/21/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Q1. 

formulating the lp function. Setting the function to maximization
```{r}
library(lpSolveAPI)
lpstock<-make.lp(0,8)
lp.control(lpstock,sense="max")
```

Since we are trying a interger programming we will set the type to integer. 
```{r}
set.objfn(lpstock,c(4,6.5,5.9,5.4,5.15,10,8.4,6.25))
set.type(lpstock,c(1:8),type = "integer")
```

Adding the constraints
```{r}
add.constraint(lpstock,c(40,50,80,60,45,60,30,25),"<=",2500000,indices = c(1:8))
add.constraint(lpstock,1000,">=",0,indices = 1)
add.constraint(lpstock,1000,">=",0,indices = 2)
add.constraint(lpstock,1000,">=",0,indices = 3)
add.constraint(lpstock,1000,">=",0,indices = 4)
add.constraint(lpstock,1000,">=",0,indices = 5)
add.constraint(lpstock,1000,">=",0,indices = 6)
add.constraint(lpstock,1000,">=",0,indices = 7)
add.constraint(lpstock,1000,">=",0,indices = 8)
add.constraint(lpstock,40,">=",100000,indices = 1)
add.constraint(lpstock,50,">=",100000,indices = 2)
add.constraint(lpstock,80,">=",100000,indices = 3)
add.constraint(lpstock,60,">=",100000,indices = 4)
add.constraint(lpstock,45,">=",100000,indices = 5)
add.constraint(lpstock,60,">=",100000,indices = 6)
add.constraint(lpstock,30,">=",100000,indices = 7)
add.constraint(lpstock,25,">=",100000,indices = 8)
add.constraint(lpstock,c(40,50,80),"<=",1000000,indices = c(1,2,3))
add.constraint(lpstock,c(60,45,60),"<=",1000000,indices = c(4,5,6))
add.constraint(lpstock,c(30,25),"<=",1000000,indices = c(7,8))
```

solving the lp problem
```{r}
solve(lpstock)
get.objective(lpstock)
get.variables(lpstock)
get.constraints(lpstock)
```
1) Determine the maximum return on the portfolio. What is the optimal number of shares to
buy for each of the stocks? What is the corresponding dollar amount invested in each
stock?
With integer restiction, the maximum return on investment is 487145.2.
The optimal number of shares to buy are S1 = 2500, S2 = 6000, S3 = 1250, H1 = 1667, H2 = 2223, H3 = 13332, C1 = 30000 and C2 = 4000 and the corresponding dollars to be invested are S1 = 100000, S2 = 300000, S3 = 100000, H1 = 100020, H2 = 100035, H3 = 799920, C1 = 900000, C2 = 100000

formulating lp problem without integer restrictions
```{r}
lpstock2 <-make.lp(0,8)
lp.control(lpstock2,sense="max")
```

```{r}
set.objfn(lpstock2,c(4,6.5,5.9,5.4,5.15,10,8.4,6.25))
```

```{r}
add.constraint(lpstock2,c(40,50,80,60,45,60,30,25),"<=",2500000,indices = c(1:8))
add.constraint(lpstock2,1000,">=",0,indices = 1)
add.constraint(lpstock2,1000,">=",0,indices = 2)
add.constraint(lpstock2,1000,">=",0,indices = 3)
add.constraint(lpstock2,1000,">=",0,indices = 4)
add.constraint(lpstock2,1000,">=",0,indices = 5)
add.constraint(lpstock2,1000,">=",0,indices = 6)
add.constraint(lpstock2,1000,">=",0,indices = 7)
add.constraint(lpstock2,1000,">=",0,indices = 8)
add.constraint(lpstock2,40,">=",100000,indices = 1)
add.constraint(lpstock2,50,">=",100000,indices = 2)
add.constraint(lpstock2,80,">=",100000,indices = 3)
add.constraint(lpstock2,60,">=",100000,indices = 4)
add.constraint(lpstock2,45,">=",100000,indices = 5)
add.constraint(lpstock2,60,">=",100000,indices = 6)
add.constraint(lpstock2,30,">=",100000,indices = 7)
add.constraint(lpstock2,25,">=",100000,indices = 8)
add.constraint(lpstock2,c(40,50,80),"<=",1000000,indices = c(1,2,3))
add.constraint(lpstock2,c(60,45,60),"<=",1000000,indices = c(4,5,6))
add.constraint(lpstock2,c(30,25),"<=",1000000,indices = c(7,8))
```


```{r}
solve(lpstock2)
get.objective(lpstock2)
get.variables(lpstock2)
get.constraints(lpstock2)
```
2) Compare the solution in which there is no integer restriction on the number of shares
invested. By how much (in percentage terms) do the integer restrictions alter the value of
the optimal objective function? By how much (in percentage terms) do they alter the
optimal investment quantities?

The return on investment is 487152.8
The number of stocks to buy are S1 = 2500,S2 = 6000,S3= 1250,H1 = 1666.667,H2= 2222.22,H3= 13333.3,C1=30000,C2=4000
The amounts to be invested are 100000, 300000, 100000, 100000, 100000, 800000, 900000, 100000 respectively.

There is a difference of $7.6 between the lp problems with and without integer restrictions.
The value of the objective function differs by 0.00156%
The investment quantities are altered as follows:
S1 = 0%, S2 = 0%, S3 = 0%, H1 = 0.03996% increased, H2 = 0.03501% decreased, H3 = 75. 01% increased and C1 = C2 = 0%
